Supporting Information Appendix:\\ Benefits and risks of diversification for individual fishers

### 2017-07-07 portfolio/text/supp.Rnw
Tweak formatting of supplement

\documentclass[12pt]{article}
\usepackage{geometry}
\geometry{verbose, letterpaper, tmargin = 2.54cm, bmargin = 2.54cm,
  lmargin = 2.54cm, rmargin = 2.54cm}
\geometry{letterpaper}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{setspace}
\usepackage{booktabs}
% \usepackage{verbatim}
% \usepackage{amsmath}
\usepackage{url}
% \usepackage{mathtools}
% \usepackage{lineno}
% \usepackage{xcolor}
% \renewcommand\linenumberfont{\normalfont\tiny\sffamily\color{gray}}
% \modulolinenumbers[2]

@@

\title{Supporting Information}

\author{
}
\date{}

@@

\begin{table}[h!]
\scriptsize
  \centering
  \caption{Labels and descriptions of unique fishing strategies. In many cases,
a particular strategy represents a group of similar permits across areas
or vessel sizes. The column ``Main species'' indicates species that make up at
least 10\% of the total revenue across all years and individuals for that
fishing strategy. ``Sock'' refers to sockeye salmon.}
  \label{tab:strategies}
  \begin{tabular}{llll}
  \toprule
\input{strategy-table.tex}
  \end{tabular}
\end{table}

>>>>

\documentclass[12pt]{article}
\usepackage{geometry}
\geometry{verbose, letterpaper, tmargin = 2.54cm, bmargin = 2.54cm,
  lmargin = 2.64cm, rmargin = 2.64cm}
\geometry{letterpaper}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{setspace}
\usepackage{booktabs}
% \usepackage{verbatim}
% \usepackage{amsmath}
\usepackage{url}
% \usepackage{mathtools}
% \usepackage{lineno}
% \usepackage{xcolor}
% \renewcommand\linenumberfont{\normalfont\tiny\sffamily\color{gray}}
% \modulolinenumbers[2]
\usepackage{lscape}

@@

\title{Supporting Information Appendix:\\
  Benefits and risks of diversification for individual fishers}

\author{
Sean C. Anderson \and
Eric J. Ward \and
Andrew O. Shelton \and
Milo D. Adkison \and
Anne H. Beaudreau \and
Richard E. Brenner \and
Alan C. Haynie \and
Jennifer C. Shriver \and
Jordan T. Watson \and
Benjamin C. Williams
}
\date{}

@@

\begin{landscape}
\begin{table}[h!]
\scriptsize
  \centering
  \caption{Labels and descriptions of unique fishing strategies. In many cases,
a particular strategy represents a group of similar permits across areas
or vessel sizes. The column ``Main species'' indicates species that make up at
least 10\% of the total revenue across all years and individuals for that
fishing strategy. ``Sock'' refers to sockeye salmon.}
  \label{tab:strategies}
  \begin{tabular}{llll}
  \toprule
\input{strategy-table.tex}
  \end{tabular}
\end{table}
\end{landscape}
